---
title: "Creating graphs in R with ggplot2"
author: "Ariel Deardorff"
date: "10/20/2020"
output: html_document
---

Loading our libraries
```{r}
library(tidyverse)
library(readxl)
library(here)
```
Loading the California National Park Data
```{r}
ca_np <- read_csv(here("data", "ca_np.csv"))
```

useful commands for exploring a dataset
```{r}
names(ca_np)
head(ca_np)
summary(ca_np)
```

loading the excel dataset for Channel Islands National Park
```{r}
ci_np <- read_excel(here("data","ci_np.xlsx"))
```

Let's investigate the visitors to Channel Island NP
```{r}
ggplot(data = ci_np, aes(x = year, y = visitors )) + geom_line()
```

store this plots as ggbase 
```{r}
gg_base <- ggplot(data = ci_np, aes(x = year, y = visitors))
```

Let's do some customizing
```{r}
gg_base + geom_point(
  color = "forestgreen",
  pch = 17,
  size = 2,
  alpha = 1
)
```

List of color names: http://sape.inf.usi.ch/quick-reference/ggplot2/colour 

Create a scatterplot where the size and color of the points are based on the number of visitors and make everything the same opacity (.5)
```{r}
ggplot(data = ci_np, aes(x = year, y = visitors, size = visitors, color = visitors)) + geom_point(alpha = .5)
```

Create a column plot fo the visitors over time where the fill color changes based on the number of visitors
```{r}
gg_base + geom_col(aes(fill = visitors))
```

